---
title: "Third Question"
author: "Maryam Shahini, Ramin Farhanian"
date: "8/9/2017"
output: 
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Question 03 (20 points)

The built-in data set called Orange in R is about the growth of orange trees. The Orange data frame has 3 columns of records of the growth of orange trees.

Variable description
Tree : an ordered factor indicating the tree on which the measurement is made. The ordering 
            is according to increasing maximum diameter.

age :  a numeric vector giving the age of the tree (days since 1968/12/31)
circumference :  a numeric vector of trunk circumferences (mm). This is probably   
                           “circumference at breast height”, a standard measurement in forestry.

Library installation on demand
```{r}
installLibrariesOnDemand <- function (packages)
{
  cat("Installing required libraries on demand:", packages , "\n")
  new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
  if(length(new.packages)) install.packages(new.packages)
  cat("Missing libraries installation is complete.", "\n")
}
installLibrariesOnDemand(c("ggplot2"))
library(ggplot2)

data("Orange")
```

Calculate the mean and the median of the trunk circumferences for different size of the trees. (Tree)

```{r}
means <-tapply(Orange$circumference, Orange$Tree, FUN=mean)
print(means)
medians<- tapply(Orange$circumference, Orange$Tree, FUN=median)
print(medians)
```

Make a scatter plot of the trunk circumferences against the age of the tree. Use different plotting symbols for different size of trees. (Tree)

```{r}
scatterPlot <- ggplot(Orange,aes(Orange$circumference, Orange$age, color= Orange$Tree, shape= Orange$Tree)) + 
  geom_point() + labs(x = "Circumference") + labs(y = "Age") + labs(shape = "Tree Group")  + labs(color = "Tree Group") +
 labs(title = "Trunk circumferences vs. age of the tree")
print(scatterPlot)
```

Display the trunk circumferences on a comparative boxplot against tree. Be sure you order the boxplots in the increasing order of maximum diameter.

```{r}
Orange$Tree <- factor(Orange$Tree, levels = as.integer(Orange$Tree[order(Orange$Tree)]))
box <- ggplot(Orange, aes( Orange$Tree, Orange$circumference)) + geom_boxplot() + labs(y = "Circumference") + labs(x = "Tree Group")
print(box)
```